### 2013-01-25 annualreports/2012/balancesheet.tex
Fix date

{\footnotesize For the financial period ended 31 March 2011 the
company was entitled to exemption from audit under section 477 of the
Companies Act 2006. No member of the company has deposited a
notice, pursuant to section 476, requiring an audit of these
financial statements under the requirements of the Companies Act
2006.

@@

Approved by the Board for issue on the 27\superscript{th} December 2012.
\vspace{48pt}

>>>>

{\footnotesize For the financial period ended 31 March 2012 the
company was entitled to exemption from audit under section 477 of the
Companies Act 2006. No member of the company has deposited a
notice, pursuant to section 476, requiring an audit of these
financial statements under the requirements of the Companies Act
2006.

@@

Approved by the Board for issue on the 14\superscript{th} January 2013.
\vspace{48pt}
